---
title: "Systematic Literature Review for Urbanism"
author: "Bayi Li"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Systematic Literature Review for Urbanism

## Using Revtools to sort out the collection of papers

https://revtools.net/data.html#importing-to-r

It can only take bib or Ris files, so we just redownload the wos collection as bib file.

```{r check working directory}
getwd()
```

Description in the paper:

> The search terms “urban resilience” and “resilient cities”

> First, Elsevier’s Scopus and Thompson Reuters Web of Science (WoS) citation databases were used to identify the literature on urban resilience over a 41-year period, beginning in 1973 (when Holling wrote his seminal article on resilience) and ending in 2013. 

> Although relatively comprehensive, these databases do not generally include books, and by focusing mainly on Englishlanguage publications,

Searching sytax:

> generate a preliminary search expression using ChatGPT

Example of question for ChatGPT could be: (Meerow et al., 2016)

—
generate query string of Scopus (Web of Science) database on the search term “urban resilience” and “resilient cities” from 1973 to 2013, excluding books and including only English-language publications
—
The return answer from GPT as following:
For Scopus database
—
( TITLE-ABS-KEY ( "urban resilience" ) OR TITLE-ABS-KEY ( "resilient cities" ) ) AND PUBYEAR > 1972 AND PUBYEAR < 2014 AND NOT DOCTYPE ( bk ) AND ( LIMIT-TO ( LANGUAGE , "English" ) )
—
For WOS database
—
TS=("urban resilience" OR "resilient cities") AND PY=1973-2013 AND LA=English NOT DT=Book
—
Using the query string recommended to search on the scopus database, we can find that 176 (Scopus) and 136 (Web of Science) are found separately. There are some deviation of amount of returned results (“The search terms “urban resilience” and “resilient cities” yielded 139 results in Scopus and 100 in WoS.”), but we can assume that it is due to the authors limited to special discipline, or the exact date of seach was conducted during a certain day of 2013. Thus, more literatures in late 2013 were not included.


In paper:

139 Scopus
100 Wos
172 After dropping the duplictes

Our search:

172 Scopus
136 WoS
247 After dropping the duplicates

```{r library}
library(revtools)
```

```{r}
# read the wos collection txt file
## data_scopus <- read.csv("./sample-data/raw-data/raw_scopus_result.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE)
# Read a text file as a data frame
## data_wos <- read.table("./sample-data/raw-data/raw_wos_result.txt", header = TRUE, sep = "\t", fill = TRUE)

data_wos <- read_bibliography("./sample-data/raw-data/raw_wos_result.bib")
# rename the column "cited_references" to "references"
colnames(data_wos)[colnames(data_wos) == "cited_references"] <- "references"

data_scopus <- read_bibliography("./sample-data/raw-data/raw_scopus_result.csv")
data_all <- merge_columns(data_wos, data_scopus)
```



```{r}
colnames(data_wos)
```
```{r}
colnames(data_scopus)
```

```{r}
matches_title <- find_duplicates(data_all, match_variable = "title", method = "lv", threshold = 2)

data_unique <- extract_unique_references(data_all, matches_title)
```

```{r}
# save the data as bib
write_bibliography(data_unique, "./sample-data/processed-data/unique_merged.bib")
# save the data as csv
write.csv(data_unique, "./sample-data/processed-data/unique_merged.csv")
```

```{r}
library(bibliometrix)
```

```{r}
# read the bib file
# data <- read_bibliography("./sample-data/processed-data/unique_merged.bib")
# read the csv file
# data <- read.csv("./sample-data/processed-data/unique_merged.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE)

data <- convert2df(file = "./sample-data/processed-data/unique_merged.csv", dbsource = "scopus", format = "csv")
```

```{r}
results <- biblioAnalysis(data)
```

```{r}

```

```{r}
```

```{r}
```

